```{r}
library(tidyverse)
df <- read_csv('data/clean/investments_w_company-info.csv')
```

In the 2021-22 fiscal year, Oberlin College’s fund managers invested more than $1.2 million in Israeli companies

```{r}
df |>
    filter(transferee_country == 'Israel') |>
    pull(amount) |>
    sum()
```

The Review’s investigation identifies more than $52 million of the College’s investments in 69 companies around the world

```{r}
# $52 million of the College's investments
df |>
    pull(amount) |>
    sum()

# 69 companies
df |>
    pull(transferee_name) |>
    unique() |>
    length()
```

The Review’s investigation found that, in the 2021-22 fiscal year, all investments in Israeli companies in the College’s portfolio were made through two branches of the same fund: Stripes Management

```{r}
df |>
    filter(transferee_country == 'Israel') |>
    pull(fund_name) |>
    unique()
```

Among the 25 firms that made investments on the College’s behalf that year

```{r}
df |>
    arrange(fund_nicename) |>
    pull(fund_nicename) |>
    unique() |>
    length()
```

only Stripes invested in Israeli companies

```{r}
df |>
    filter(transferee_country == 'Israel') |>
    pull(fund_name) |>
    unique()
```

Stripes invested a total of $2.1 million on the College’s behalf

```{r}
df |>
    filter(fund_nicename == 'Stripes Offshore') |>
    pull(amount) |>
    sum()
```

of which 60% ($1.2 million) went to Israeli companies

```{r}
df |>
    filter(fund_nicename == 'Stripes Offshore') |>
    group_by(transferee_country) |>
    summarize(
        amount = sum(amount),
    ) |>
    ungroup() |>
    mutate(
        percent = amount / sum(amount)
    ) |>
    arrange(desc(amount))
```

The remaining $0.9 million went to four companies in Canada, Germany, and the United Kingdom, respectively

```{r}
# the remaining $0.9 million
df |>
    filter(fund_nicename == 'Stripes Offshore') |>
    filter(transferee_country != 'Israel') |>
    pull(amount) |>
    sum()

# four companies in Canada, Germany, and the United Kingdom
df |>
    filter(fund_nicename == 'Stripes Offshore') |>
    filter(transferee_country != 'Israel') |>
    group_by(transferee_country) |>
    summarize(num_comps = length(unique(transferee_name)))
```

Israeli companies made up about 7 percent of the College’s indirect foreign investments in the 2021–--22 fiscal year.

```{r}
df |>
    filter(!is_direct) |>
    group_by(transferee_country) |>
    summarize(
        amount = sum(amount)
    ) |>
    mutate(percent = amount / sum(amount)) |>
    filter(transferee_country == 'Israel')
```

The documents detail financial holdings in a total of 64 companies managed through 25 funds

```{r}
# 69 companies
df |>
    filter(!is_direct) |>
    pull(transferee_name) |>
    unique() |>
    length()

df |>
    pull(fund_nicename) |>
    unique() |>
    length()
```

totaling a combined $17.5 million

```{r}
df |>
    filter(!is_direct) |>
    pull(amount) |>
    sum()
```

The College invested an additional $35 million directly in five funds

```{r}
# 38 million
df |>
    filter(is_direct) |>
    pull(amount) |>
    sum()

# five funds
df |>
    filter(is_direct) |>
    pull(fund_name) |>
    unique() |>
    length()
```

all of them incorporated in the Cayman Islands

```{r}
df |>
    filter(is_direct) |>
    pull(transferee_country) |>
    unique()
```

Software and tech ventures led the College’s portfolio, with more than $3 million invested in companies in that sector

```{r}
df |>
    group_by(sector) |>
    summarize(amount = sum(amount)) |>
    arrange(desc(amount))
```

A further $1.4 million went to cryptocurrency and stock trading platforms

```{r}
df |>
    group_by(sector) |>
    summarize(amount = sum(amount)) |>
    filter(sector == 'Cryptocurrency & Stock')
```

$1.3 million to companies that develop mobile apps or games

```{r}
df |>
    group_by(sector) |>
    summarize(amount = sum(amount)) |>
    filter(sector == 'Mobile Apps')
```

In June of 2021, the College’s fund managers purchased a $873,000 stake in Paper Education Company, Inc

```{r}
df |>
    filter(transferee_name == 'Paper Education Company Inc') |>
    select(transferee_name, date, amount)
```

Among the College’s other notable investments are the period-tracking app Clue ($161,000)

```{r}
df |>
    filter(transferee_name == 'Clue By Biowink GmbH') |>
    select(transferee_name, amount)
```

and Rei Do Pitaco Limited ($160,000)

```{r}
df |>
    filter(transferee_name == 'Rei Do Pitaco Limited') |>
    select(transferee_name, amount)
```

The College’s fund managers invested heavily in companies in Europe, with more than $10.8 million distributed to 36 companies in that region

```{r}
df |>
    filter(!is_direct) |>
    group_by(region) |>
    summarize(
        amount = sum(amount),
        num_comps = length(unique(transferee_name))
    ) |>
    arrange(desc(amount))
```

North and South America followed, with a combined $3.5 million invested across 14 companies

```{r}
df |>
    filter(!is_direct) |>
    filter(region %in% c('North America', 'South America')) |>
    summarize(
        amount = sum(amount),
        num_comps = length(unique(transferee_name))
    )
```