```{r}
library(tidyverse)
df <- read_csv('data/clean/investments_w_company-info.csv')
```

In 2021, Oberlin College’s fund managers invested more than $1.2 million in Israeli companies

```{r}
df |>
    mutate(date = mdy(date)) |>
    filter(year(date) == 2021) |>
    filter(transferee_country == 'Israel') |>
    pull(amount) |>
    sum()
```

The Review’s investigation identifies more than $52 million of the College’s investments 

```{r}
df |>
    pull(amount) |>
    sum()
```

in 69 entities around the world

```{r}
df |>
    pull(transferee_name) |>
    unique() |>
    length()
```

The four Israeli companies — Fireblocks, MobiLesson, Orca Security, and Cyber Hunters — are all part of the Israeli tech sector

```{r}
df |>
    filter(transferee_country == 'Israel') |>
    pull(sector) |>
    unique()
```

in 2021, all investments in Israeli companies in the College’s portfolio were made through two funds managed by the same firm: Stripes Management

```{r}
df |>
    filter(transferee_country == 'Israel') |>
    pull(fund_name) |>
    unique()

df |>
    filter(transferee_country == 'Israel') |>
    pull(fund_nicename) |>
    unique()
```

Among the 25 firms that made investments on the College’s behalf that year, 

```{r}
df |>
    pull(fund_nicename) |>
    unique() |>
    length()
```

only Stripes invested in Israeli companies

```{r}
df |>
    filter(transferee_country == 'Israel') |>
    pull(fund_nicename) |>
    unique()
```

Stripes invested a total of $2.1 million on the College’s behalf

```{r}
df |>
    filter(fund_nicename == 'Stripes Management') |>
    pull(amount) |>
    sum()
```

of which 60 percent ($1.24 million) went to Israeli companies

```{r}
df |>
    filter(fund_nicename == 'Stripes Management') |>
    group_by(transferee_country) |>
    summarize(amount = sum(amount)) |>
    mutate(percent = amount / sum(amount)) |>
    arrange(desc(amount))
```

The remaining $0.9 million went to four companies in Canada, Germany, and the United Kingdom, respectively

```{r}
df |>
    filter(fund_nicename == 'Stripes Management') |>
    filter(transferee_country != 'Israel') |>
    pull(amount) |>
    sum()

df |>
    filter(fund_nicename == 'Stripes Management') |>
    filter(transferee_country != 'Israel') |>
    pull(transferee_country) |>
    unique()

df |>
    filter(fund_nicename == 'Stripes Management') |>
    filter(transferee_country != 'Israel') |>
    pull(transferee_name) |>
    unique() |>
    length()
```

Israeli companies made up 7 percent of the College’s indirect foreign investments

```{r}
df |>
    filter(!is_direct) |>
    group_by(transferee_country) |>
    summarize(amount = sum(amount)) |>
    mutate(percent = amount / sum(amount)) |>
    ungroup() |>
    filter(transferee_country == 'Israel')
```

The documents detail financial holdings in a total of 64 foreign companies

```{r}
df |>
    filter(!is_direct) |>
    pull(transferee_name) |>
    unique() |>
    length()
```

managed through 20 funds

```{r}
df |>
    filter(!is_direct) |>
    pull(fund_nicename) |>
    unique() |>
    length()
```

totaling a combined $17.5 million

```{r}
df |>
    filter(!is_direct) |>
    pull(amount) |>
    sum()
```

The College invested an additional $35 million directly in five funds

```{r}
df |>
    filter(is_direct) |>
    pull(amount) |>
    sum()
```

all of them incorporated in the Cayman Islands

```{r}
df |>
    filter(is_direct) |>
    pull(transferee_country) |>
    unique()
```

The College invested at least $4.6 million in software and tech ventures

```{r}
df |>
    filter(sector == 'Software & Tech') |>
    pull(amount) |>
    sum()
```

and at least $1.4 million in cryptocurrency and stock trading platforms

```{r}
df |>
    filter(sector == 'Cryptocurrency & Stock') |>
    pull(amount) |>
    sum()
```

In June 2021, the College’s fund managers invested $873,406 in Paper Education Company, Inc

```{r}
df |>
    filter(transferee_name == 'Paper Education Company Inc') |>
    select(transferee_name, date, amount)
```

Among the College’s other notable investments are the period-tracking app Clue ($161,483)

```{r}
df |>
    filter(grepl('Clue', transferee_name)) |>
    select(transferee_name, amount)
```

and Rei Do Pitaco Limited ($159,806)

```{r}
df |>
    filter(grepl('Rei Do Pitaco', transferee_name)) |>
    select(transferee_name, amount)
```

The College’s fund managers invested heavily in companies in Europe, with more than $10.8 million distributed to 36 companies in that region

```{r}
df |>
    filter(!is_direct) |>
    group_by(region) |>
    summarize(
        amount = sum(amount),
        num_comps = length(unique(transferee_name))
    ) |>
    ungroup() |>
    filter(region == 'Europe')
```

North and South America followed, with a combined $3.3 million invested across 13 companies

```{r}
df |>
    filter(!is_direct) |>
    group_by(region) |>
    summarize(
        amount = sum(amount),
        num_comps = length(unique(transferee_name))
    ) |>
    ungroup() |>
    filter(region %in% c('North America', 'South America'))

df |>
    filter(!is_direct) |>
    filter(region %in% c('North America', 'South America')) |>
    pull(amount) |>
    sum()
```